rbeast2: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-16 article.tex
Removed comma
Rewrote Examples

\verb;rbeast2;'s main function is \verb;run_beast2;, which, 
configures BEAST2, runs it and parses its output. 
\verb;run_beast2; needs at least the name of a 
FASTA file containing a DNA alignment. 
The default settings for the other arguments of \verb;run_beast2; 
are identical to BEAUti's and BEAST2's default settings.
Per alignment, a site model, clock model and tree prior can be chosen.
Multiple alignments can be used, each with its own (unlinked) site model, 
clock model and tree prior.

@@

BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
to produce a BEAST2 configuration file. 
In BEAUti, this is achieved by loading a FASTA file, 
then saving an output file using a common
save file dialog. After this, BEAST2 needs to be invoked
on the created configuration file to create multiple files
storing the created posterior. Finally, these output
files must be parsed by either Tracer of DensiTree.

@@

This code will create a (temporary) BEAST2 configuration file,
using a FASTA file with name \verb;alignment.fas;, 
using the same default settings as BEAUti.
\verb;rbeast2; will then execute BEAST2 with that file, and
parses the output. The output, named \verb;out;, is a list of
parameter estimates, posterior phylogenies (one for each alignment)
and operator acceptances.

@@

The following script shows how to do this in \verb;rbeast2;:

@@

\verb;rbeast2; allows for the same functionality of Tracer. 
Tracer, among others, shows the effective sample
sizes of each posterior's variables. As an MCMC run needs to
converge first, Tracer discards the first 10\% of all parameter
estimates. This is called the "burn-in". To remove the burn-in
in \verb;rbeast2;:

@@

Then, to calculate the effective sample sizes in \verb;rbeast2;:

@@

Tracer displays multiple summary statistics for each
estimated variable: the mean and its standard error, standard deviation,
variance, median, mode, geometric mean, 95\% highest posterior density interval, 
auto-correlation time and effective sample size. To obtain all these summary statistics 
of, for example, the estimated birth rate in \verb;rbeast2;:

\begin{lstlisting}[language=R, floatplacement=H]
sum_stats <- calc_summary_stats(
  traces$birthRate, 
  sample_interval = 1000
)
\end{lstlisting}

\verb;rbeast2; allows for the same functionality of DensiTree.
DensiTree displays the phylogenies in a posterior at the same
time scale over one another, allowing to see the uncertainty in
topology and branch lengths. To visualize the same in \verb;rbeast2;:

>>>>

\verb;rbeast2;'s main function is \verb;run_beast2;, which
configures BEAST2, runs it and parses its output. 
\verb;run_beast2; needs at least the name of a 
FASTA file containing a DNA alignment. 
The default settings for the other arguments of \verb;run_beast2; 
are identical to BEAUti's and BEAST2's default settings.
Per alignment, a site model, clock model and tree prior can be chosen.
Multiple alignments can be used, each with its own (unlinked) site model, 
clock model and tree prior.

@@

BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
to produce a BEAST2 configuration file. 
In BEAUti, this is achieved by loading a FASTA file, 
then saving an output file using a common
save file dialog. After this, BEAST2 needs to be invoked
on the created configuration file to create multiple files
storing the posterior created by BEAST2. Finally, these output
files must be parsed by either Tracer of DensiTree.

@@

This code will create a (temporary) BEAST2 configuration file,
from the FASTA file with name \verb;alignment.fas;, 
using the same default settings as BEAUti.
\verb;rbeast2; will then execute BEAST2 using that file, and
parses the output. The returned data structure, named \verb;out;, 
is a list of parameter estimates, posterior phylogenies (one for each alignment)
and operator acceptances.

@@

To do this in \verb;rbeast2;:

@@

\verb;rbeast2; allows for the same functionality of Tracer.
Tracer works on the values of the parameter estimates sampled
in the BEAST2 run. This is called the "trace" (hence the name).
The start of the trace is usually discarded, as an MCMC 
algorithm (such as used by BEAST2) first has to converge to
its equilibrium. The start of the trace, called the "burn-in", 
will be removed, as its parameter estimates are not 
representative. By default, Tracer discards the first 10\% of all 
the parameter estimates.

To remove the burn-in from all parameter estimates in \verb;rbeast2;:

@@

Tracer shows the ESSes of each posterior's variables.
These ESSes are important to determine the strength of the
inference. As a rule of thumb, an ESS of 200 is acceptable 
for any parameter estimate.

To calculate the effective sample sizes (of all estimated variables) in \verb;rbeast2;:

@@

Tracer displays multiple summary statistics for each
estimated variable: the mean and its standard error, standard deviation,
variance, median, mode, geometric mean, 95\% highest posterior density interval, 
auto-correlation time and effective sample size. It displays these statistics per
variable. In \verb;rbeast2;, these summary statistics are collected for
all estimated parameters at once:

\begin{lstlisting}[language=R, floatplacement=H]
sum_stats <- calc_summary_stats(
  traces, 
  sample_interval = 1000
)
\end{lstlisting}

\verb;rbeast2; allows for the same functionality as DensiTree.
DensiTree displays the phylogenies in a posterior at the same
time scale, drawn one over one another, allowing to see the uncertainty in
topology and branch lengths. To do so in \verb;rbeast2;:
